Pillar 2 - Topic Modeling

### 2019-01-18 Pillar 2 - Topic Modeling.Rmd
minor changes

# Setup
```{r load data}
load("data_pillar_2.RDATA")
```

@@

```{r, cache = TRUE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

@@

## Results
```{r LDA prepare}
prepare_data_LDA_beta <- function(results){

@@

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = facet)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

```{r, cache = TRUE}
# Bet Distribution
LDA_description_10 %>%
  prepare_data_LDA_beta %>%
  visualize_LDA_beta

# Gamma Distribution 1
LDA_description_10 %>%
  prepare_data_LDA_gamma(level = Cluster) %>%
  visualize_LDA_gamma1

# Gamma Distribution 2
LDA_description_10 %>%
  prepare_data_LDA_gamma(level = Cluster) %>%
  visualize_LDA_gamma2
```

```{r}
visualize_LDA <- function(data, level = Course, id_plot = "test"){

@@

```{r}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA(level = Course,
                  id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA(level = Cluster,
                  id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA(level = Concentration,
                  id_plot = paste(id_plot, "_concentration"))

@@

```{r, cache = TRUE}
LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")

@@

```{r visualization LDA, eval = F}

visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))

>>>>

# Setup
```{r import data}
load("data_pillar_2.RDATA")
```

@@

```{r LDA fit, cache = TRUE}
LDA_description_10 <- LDA(d_description_cast, k = 10, control = list(seed = 123))
LDA_description_17 <- LDA(d_description_cast, k = 17, control = list(seed = 123))
LDA_description_25 <- LDA(d_description_cast, k = 25, control = list(seed = 123))

@@

```{r LDA save models}
save(LDA_description_10, LDA_description_17, LDA_description_25,
     LDA_overview_10, LDA_overview_17, LDA_overview_25,
     LDA_manual_10, LDA_manual_17, LDA_manual_25,
     file = "LDA.RDATA")
```

## Visualization
### Functions
```{r LDA prepare}
prepare_data_LDA_beta <- function(results){

@@

  data_prepared %>%
    ggplot(aes(reorder_within(facet, 
                              by = gamma, 
                              within = topic), 
               y = gamma, 
               fill = topic)) +
    geom_col(show.legend = F) +
    facet_wrap(~ topic, 
               scales = "free") +
    scale_x_reordered() +
    coord_flip() +
   # labs(x = ensym(facet), y = "Gamma", title = paste("Main", ensym(facet), "of each Topic") +
    theme_light() +
    theme(axis.text.x = element_text(angle = 90, hjust = 0),
          plot.title = element_text(hjust = 0.5))

@@

```{r LDA visualize all distrib}
visualize_LDA_all_distrib <- function(data, level = Course, id_plot = "test"){

@@

```{r LDA visualize all level}
visualize_LDA_all_level <- function(data, id_plot = "test"){

  data %>% 
    visualize_LDA_all_distrib(level = Course,
                              id_plot = paste(id_plot, "_course"))

  data %>% 
    visualize_LDA_all_distrib(level = Cluster,
                              id_plot = paste(id_plot, "_cluster"))

  data %>% 
    visualize_LDA_all_distrib(level = Concentration,
                              id_plot = paste(id_plot, "_concentration"))

@@

### Plots
```{r LDA plot, cache = TRUE}
LDA_description_10 %>% visualize_LDA_all_level(id_plot = "description_k10")
LDA_description_17 %>% visualize_LDA_all_level(id_plot = "description_k17")
LDA_description_25 %>% visualize_LDA_all_level(id_plot = "description_k25")

@@

```{r label, eval = F}
tidy(LDA_manual_10, "beta") %>%
  filter(beta > 1e-3) %>%
  bind_tf_idf(term = term, document = topic, n = beta) %>%
  group_by(topic) %>%
  top_n(10, tf_idf) %>%
  arrange(topic, desc(tf_idf))

  count(term, topic) %>%
  arrange(desc(n)) %>%

  filter(beta > 1e-3) %>%
  group_by(term) %>%
    mutate(n_topic = n(),
           beta = beta / n_topic) %>%
  group_by(topic) %>%
    top_n(10, beta)

  count(topic, term, wt = beta) %>%
  (term = term, document = topic, n = n) %>%
  group_by(topic) %>%
  top_n(10, tf_idf)

  group_by(term) %>%
  summarise(beta = sum(beta)) %>%
  arrange(desc(beta))

labels <- list(
  description_10 = "X"
)
```

```{r label bis, eval = FALSE}
visualize_LDA(LDA_cluster_10, id_plot = "Cluster, k = 10 with labelled topics", facet = T,
              topic_names = c("Psychology & Information", "Economics and Development", "Biology", "Chemistry and Math",
                              "Sociology", "Law", "Research", "International Politics",
                              "Philosophy", "Humanities"))
